{ \fontfamily{ptm}\selectfont Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method }

### 2025-10-27 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

    Now, it only remains to determine the sequence $\alpha_k$ to derive a type of convergence rate for the algorithm because from the above theorem, we have the convergence rate $\beta_k$ and, the error parameters $\epsilon_k, \rho_k$ both controlled by the sequence $(\alpha_k)_{k \ge 0}$.

@@

                \item Let $v_0\in\dom \omega^\star$ be a feasible initial guess of $\Psi_{\lambda}$, and let $\tau > \Vert AA^\top\Vert$ be the inverse stepsize. 

@@

            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$. 

@@

            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_n^{(k)}, v_n^{(k)}\right)_{n\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\bar \lambda, \underline \lambda, \gamma^\circ$. 

@@

                \item All the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ must have $\sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$. 
                \item There exists smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$. 

@@

            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_n^{(k)}, v_{n}^{(k)}\right)_{n \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and $C_1$ satisfies Assumption \ref{ass:bounded-inn-cmplx}. 

@@

                \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so $\sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$. 
                \item There exists a constant $C_1$ that bounds the optimality gap of all initial guesses: 
                    \infty > C_1 \ge  \sup_{k \in \N \cup \{0\}}\left\lbrace

@@

                \item\label{prop:inner-lp-cmplx-result3} 

@@

@@

                        2\frac{\log(\epsilon/C_2)}{
                            \log\left(
                                1 - \frac{\gamma^{\min}}{2\lambda^{\max}}

@@

            After some algebra it can be shown that $\Psi_\lambda^{(k)}(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
            From then on it's direct and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 

@@

            By its definition in \eqref{eqn:primal-pp-k}, $\forall k \ge 0$ it satisfies $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\min}$. 
            And since $\lambda^{(k)}$ is finite, it has $\sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item1} and it's sufficient to have $C_1 = \Psi_{\lambda^{\max}}^{(k)}$

@@

>>>>

    \begin{proposition}[generic convergence rate of the gradient mapping]\;\label{prop:apg-cnvg-gm-generic}\\
        \todoinline{Cette propositions ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }

    \end{proof}
    \par
    Now, it only remains to determine the sequence $\alpha_k$ to derive a type of convergence rate for the algorithm because from the above theorem, we have the convergence rate $\beta_k$ and, the error parameters $\epsilon_k, \rho_k$ both controlled by the sequence $(\alpha_k)_{k \ge 0}$.

@@

                \item Let $v_0\in\dom \omega^\star$ be a feasible initial guess of $\Psi_{\lambda}$, and let $\tau \ge \lambda\Vert AA^\top\Vert$ be the inverse step size. 

@@

            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$. 

@@

            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_n^{(k)}, v_n^{(k)}\right)_{n\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$. 

@@

                \item There exists a constant $C_0$ such that all the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ satisfies $C_0 = \sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$. 
                \item There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$. 

@@

            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_n^{(k)}, v_{n}^{(k)}\right)_{n \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:bounded-inn-cmplx}. 

@@

                \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so, there exists $L_\Phi^{\max}$ such that $L_\Phi^{\max} = \sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$. 
                \item\label{prop:inner-lp-cmplx-result3} There exists a constant $C_1$ that bounds the optimality gap of all initial guesses: 
                    \infty > C_1 \ge  \sup_{k \in \N \cup \{0\}}

@@

@@

                \item\label{prop:inner-lp-cmplx-result5} 

@@

                        \frac{2\ln(\epsilon/C_2)}{
                            \ln\left(
                                1 - \frac{\gamma^{\min}}{2\lambda^{\max}\left\Vert AA^\top\right\Vert}

@@

            After some algebra it can be shown that $\Psi_\lambda(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
            From then on it's direct, and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 

@@

            By its definition in \eqref{eqn:primal-pp-k}, $\forall k \ge 0$ it satisfies $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\max}$. 
            And since $\lambda^{(k)}$ is finite, it has $L^{\max}_\Phi = \sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item1}, \ref{prop:inn-looplin-cnvg-item2} and, $C_0 = \sup_{k \in \{0\}\cup \N} \left\Vert v_0^{(k)} - \bar v^{(k)} \right\Vert < \infty$ from Assumption \ref{ass:bounded-inn-cmplx}, then it's sufficient to have: $C_1 = L_{\Phi}^{\max} C_0$ by $L^{(k)}_\Phi$ Lipschitz continuity of $\Phi_\lambda^{(k)}$. 
            To see \ref{prop:inn-looplin-cnvg-item4}, use all previous results \ref{prop:inn-looplin-cnvg-item3}, \ref{prop:inn-looplin-cnvg-item2} and, then it's sufficient to have $C_2 = \sqrt{C_1}\left(L^{\max}_\Phi\sqrt{2\lambda^{\max}} + \sqrt{C_1}\right)$. 
            And finally, we are ready to show \ref{prop:inner-lp-cmplx-result5}, it has for all $k \ge 0$: 
                & \mathbf G_\lambda^{(k)}(z_n^{(k)}, v_n^{(k)}) 
                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
                \right)^{n/2}
                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
                    \sqrt{\Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})}
                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
                \right)^{n/2}
                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
                    \sqrt{C_1}
                \right)\sqrt{C_1}
                &\underset{(3)}{\le}
                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
                \right)^{n/2} C_2
                &\underset{(4)}{\le}
                    1 - \frac{\gamma^{\min}}{2 \lambda^{\max}\Vert AA^\top\Vert}
                \right)^{n/2} C_2. 
            At (1), we used Theorem \ref{prop:inn-loop-lin-cnvg}. 
            At (2), we used results form \ref{prop:inner-lp-cmplx-result3} and, at (3) we used \ref{prop:inner-lp-cmplx-result4}. 
            Finally, at (4), we use the fact that the step size $\tau$ in Definition \ref{def:ista-inner-lp} which translate into our context, it has $\tau^{(k)} \ge \lambda^{(k)}\Vert AA^\top\Vert$, and hence it can be upper bounded by $\tau^{\max} := \sup_{k \in \N \cup \{0\}}\lambda^{(k)}\Vert AA^\top\Vert < \infty$. 
            Now, substitute $n = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_n^{(k)}, v_n^{(k)}\right) \le \epsilon$ by using the log of base formula. 

@@

    \subsection{Overall complexity}
        In this section we combine the complexity of the inner loop with the convergence rate of the outer loop to deduce the rate of convergence. 
        Details will be given to the assumptions needed to obtain globally bounded complexity of the inner loop.
